\section{Project work}
%\addcontentsline{toc}{section}{\numberline{}7 - Project work}
This section will describe all the work accomplished by the student in this specialization project. The project has lasted for 93 week days and has been continually worked on from the start, albeit in parallel with other courses as usual for this kind of project. 
\\\\

\noindent
\textit{\color{red}\Big{Your work:}\\
N chapters describing your own work. It can be natural to use a tree structure, where the first chapter gives an overall introduction and the remaining chapters with sub-chapters describes details. In some cases it is natural to partition procedure and results in different chapters, in other cases this is not natural.}\\


\subsection{Measurements/Measurement tools}
%\addcontentsline{toc}{subsection}{\numberline{}7.1 - Measurement/Measurement tools}
Valgrind tools, other tools, principles, etc. Maybe add more subsections because of this. \\

\subsubsection{Callgrind}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.1.1 - Callgrind}
Basic information, what it can be used for. \\

\subsubsection{Massif}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.1.2 - Massif}
Basic information, what it can be used for. \\

\subsubsection{etc}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.1.3 - etc}
etc\\\\\\

\subsection{Results}
%\addcontentsline{toc}{subsection}{\numberline{}7.2 - Results}
Measurement results. \\

\subsubsection{Callgrind results}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.2.1 - Callgrind results}
Presented with graphs, tables (maybe in 11 - Appendix if too big), figures etc, and written in a more or less straight forward way. Elaboration saved for 8 - Discussion.\\

\subsubsection{Massif results}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.2.2 - Massif results}
Presented with graphs, tables (maybe in 11 - Appendix if too big), figures etc, and written in a more or less straight forward way. Elaboration saved for 8 - Discussion.\\

\subsubsection{etc}
%\addcontentsline{toc}{subsubsection}{\numberline{}7.2.3 - etc}
etc\\\\\\

\subsubsection{Suggested HW/SW Co-design methodology}
%\addcontentsline{toc}{subsection}{\numberline{}7.3 - Suggested HW/SW Co-design methodology}
Description of methodology in detail, probably with more subsections. Maybe even include
\\


\clearpage